\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-25 tex/ms.tex
tensorflow description

We therefore construct a design matrix $\mathbf{B}$ out of the PLD basis. To
increase the flexibility of the systematics model, we append to $\mathbf{B}$ 5 orthogonal
polynomials in time for each of the two orbits of \tess in each sector.
The systematics model $\mathbf{b}$ for the $n^\mathrm{th}$ signal is thus
%
\begin{align}
\mathbf{b}_n = \mathbf{B} \mathbf{w}_n
\end{align}
%
where $\mathbf{w}_n$ are the weights of each regressor.
Since we solve for different weights for each of the 75 light curves in Sector 1
and 20 light curves in Sector 2, our systematics model has
$75 \times (75 + 2 \times 5) + 20 \times (20 + 2 \times 5) = 6,975$ free parameters.
The total number of data points is $912,605$, so overfitting is not particularly
concerning; nevertheless, we impose an L2 prior on the weights with
standard deviation $\sigma_B = 0.1$ (see \S\ref{sec:model}).

@@

As with the systematics model (\S\ref{sec:systematics}), the model
for the astrophysical signal is \emph{linear}: the total signal $\mathbf{a}$ 
is a linear operation on the vector of spherical harmonic coefficients 
that describes the body's surface:
%
\begin{align}
    \mathbf{a} = \mathbf{A} \mathbf{y}
\end{align}
%
where $\mathbf{A}$ is the design matrix \citep[equal to the quantity 
$\mathbf{s}^\top\mathcal{A}\mathbf{R}'\mathbf{R}$ in][]{Luger2019}
and $\mathbf{y}$ is the vector of spherical harmonic coefficients. 
Note that in \cite{Luger2019}, $\mathbf{y}$ describes the emissivity of the surface,
but here we will use it to represent the \emph{albedo} of the planet.
As we will see below, the linearity of the problem makes it easily invertible.

@@

Our full model for each light curve is simply the product of the 
systematics model $\mathbf{b}_n$ (different for each target) and
the \starry model $\mathbf{a}$ (shared by all targets). Since we happen
to know the exact distance $\mathbf{r}$ between \tess and Sol d at all times
(\S\ref{sec:orbit}), we also include the inverse square of $\mathbf{r}$ 
as a multiplicative term. The model for the flux timeseries
in the $n^\mathrm{th}$ postage stamp is therefore
%
\begin{align}
    \label{eq:model}
    \mathbf{m}_n = (\mathbf{r}^{-2}) \circ (\mathbf{B} \mathbf{w}_n) \circ (\mathbf{A} \mathbf{y})
\end{align}
%
where $\circ$ denotes the element-wise product of two vectors.

@@

In general, we find that the iterative scheme converges within about 50 
iterations. However, since it is strongly regularized, the model significantly
underfits the data. In the next step, we remove our L2 prior on the spherical
harmonic coefficients and instead regularize the actual surface albedo, which
we compute on a uniform spherical grid with 50,000 points. We enforce a 
uniform prior in the range $[0, 1]$, with an exponential drop on either 
side. This constraint breaks the linearity of the problem, so we must
now use a non-linear optimizer.

@@

\acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully 
acknowledge Dan Foreman-Mackey, David W Hogg, Ben Pope, \todo{and ...} 
for useful conversations. Crucial parts of this work were carried out at the 
TESS Data Workshop, hosted by Space Telescope Science Institute, and the 
Building Early Science with TESS Workshop, hosted by the University of Chicago.}
\facility{TESS}
\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, TensorFlow, \spiceypy \citep{Annex2019}}
% Bibliography
\pagebreak
\bibliography{bib}

>>>>

We therefore construct a design matrix $\mathbf{B}$ out of the PLD basis. To
increase the flexibility of the systematics model, we append to $\mathbf{B}$ 5 orthogonal
polynomials in time for each of the two orbits of \tess in each sector.
The systematics model $\mathbf{p}$ for the $n^\mathrm{th}$ signal is thus
%
\begin{align}
\mathbf{p}_n = \mathbf{B} \mathbf{w}_n
\end{align}
%
where $\mathbf{w}_n$ are the weights of each regressor.
Since we solve for different weights for each of the 75 light curves in Sector 1
and 20 light curves in Sector 2, our systematics model has
$75 \times (75 + 2 \times 5) + 20 \times (20 + 2 \times 5) = 6,975$ free parameters.
The total number of data points is $912,605$, so overfitting is not particularly
concerning; nevertheless, we impose an L2 prior on the weights with
standard deviation $\sigma_B = 0.1$ (see \S\ref{sec:model}).

@@

As with the systematics model (\S\ref{sec:systematics}), the model
for the astrophysical signal is \emph{linear}: the signal $\mathbf{s}$ 
is a linear operation on the vector of spherical harmonic coefficients 
that describes the body's surface:
%
\begin{align}
    \mathbf{s} = \mathbf{A} \mathbf{y}
\end{align}
%
where $\mathbf{A}$ is the design matrix and $\mathbf{y}$ is the vector of spherical harmonic coefficients. 
Note that in \cite{Luger2019}, $\mathbf{y}$ describes the emissivity of the surface,
but here we will use it to represent the \emph{albedo} of the planet.
We choose a maximum spherical harmonics degree $l_{max} = 15$ for our fits,
noting that increasing $l_{max}$ above this value does not significantly
improve the quality of our fits. At the equator, $l = 15$ corresponds to
a resolution on the order of $180^\circ/15 = 12^\circ$.

@@

Our full model for each light curve is simply the product of the 
systematics model $\mathbf{p}_n$ (different for each target) and
the \starry model $\mathbf{s}$ (shared by all targets). Since we happen
to know the exact distance $\mathbf{r}$ between \tess and Sol d at all times
(\S\ref{sec:orbit}), we also include the inverse square of $\mathbf{r}$ 
as a multiplicative term. The model for the flux timeseries
in the $n^\mathrm{th}$ postage stamp is therefore
%
\begin{align}
    \label{eq:model}
    \mathbf{m}_n = (\mathbf{r}^{-2}) \circ (\mathbf{B} \mathbf{w}_n) \circ (\mathbf{A} \mathbf{y})
\end{align}
%
where $\circ$ denotes the element-wise product of two vectors.

@@

In general, we find that the iterative scheme converges within about 50 
iterations. However, since it is strongly regularized, the model significantly
underfits the data. In the second step, we remove our L2 prior on the spherical
harmonic coefficients and instead regularize the actual surface albedo, which
we compute on a uniform spherical grid with 50,000 points. We enforce a 
uniform prior in the range $[0, 1]$, with an exponential drop on either 
side. We additionally impose a constraint on the power spectrum of the
inferred map, \todo{bla bla}.

Our full negative log likelihood function in this step is therefore
%
\begin{align}
    -\log\mathcal{L} \, = \, 
        &\frac{1}{2}(\mathbf{f} - \mathbf{m})^\top \Sigma^{-1} (\mathbf{f} - \mathbf{m}) \, + \nonumber \\
        &\frac{1}{2}\mathbf{w}^\top \Lambda_w^{-1} \mathbf{w} \, + \nonumber \\
        &\frac{1}{2}(\mathbf{a_-} + 1 - \mathbf{a_+})^\top \Lambda_a^{-1} (\mathbf{a_-} + 1 - \mathbf{a_+}) \, + \nonumber \\
        &\frac{1}{2}(\rho - l^{-\gamma})^\top \Lambda_\rho^{-1} (\rho - l^{-\gamma}) \, + \nonumber \\
        &\frac{1}{2} \frac{\gamma^2}{\sigma_\gamma^2}
        \quad,
\end{align}
%
where \todo{explain all this stuff.}

All of these constraint break the linearity of the problem, so we must
now use a non-linear optimizer. We use the 
\textsf{AdamOptimizer} method in the \tf package \citep{Abadi2015}
to maximize the negative log likelihood.

@@

\acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully 
acknowledge Dan Foreman-Mackey, David W Hogg, Ben Pope, \todo{and ...} 
for useful conversations. Crucial parts of this work were carried out at the 
TESS Data Workshop, hosted by Space Telescope Science Institute, and the 
Building Early Science with TESS Workshop, hosted by the University of Chicago.}
\facility{TESS}
\software{Astropy, Matplotlib, Numpy, \starry \citep{Luger2019}, 
TensorFlow \citep{Abadi2015}, \spiceypy \citep{Annex2019}}
% Bibliography
\pagebreak
\bibliography{bib}
